%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Twenty Seconds Resume/CV
% LaTeX Template
% Version 1.1 (8/1/17)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Carmine Spagnuolo (cspagnuolo@unisa.it) with major modifications by
% Vel (vel@LaTeXTemplates.com)
%
% Adapted to be an Rmarkdown template by Rob J Hyndman
% 23 November 2018
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,a4paper,]{twentysecondcv}

\usepackage[scaled=0.86]{DejaVuSansMono}

\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{csquotes}

\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

\usepackage{booktabs}



%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------

% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}

% Profile pic
\profilepic{}

\cvname{Cade Abrams} % Your name

\cvjobtitle{Postdoctoral Research Fellow} % Job title/career
\cvdate{September 2023} % Date of birth or date of CV??
\cvaddress{Department of Educational and Developmental
Science} % Short address/location, use \newline if more than 1 line is required
\cvpronouns{} % Pronouns
\cvnumberphone{+1(864)-993-8064} % Phone number
\cvsite{} % Personal website
\cvmail{\href{mailto:tcabrams@email.sc.edu}{\nolinkurl{tcabrams@email.sc.edu}}} % Email address
\cvtwitter{}
\cvgithub{\href{https://github.com/Tcabrams44}{Tcabrams44}}
\cvlinkedin{\href{https://www.linkedin.com/in/cade-abrams-phd}{cade-abrams-phd}}
\cvorcid{}
\cvscholar{}
\cvresearchgate{}

\lfoot{\sf Curriculum Vitae: Cade Abrams}
\rfoot{\sf\thepage}

% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}
\aboutme{Fill this in.}

% Skill bar section, each skill must have a value between 0 an 6 (float)
%\skills{{pursuer of rabbits/5.8},{good manners/4},{outgoing/4.3},{polite/4},{Java/0.01}}

% Skill text section, each skill must have a value between 0 an 6
%\skillstext{{lovely/4},{narcissistic/3}}

\makeprofile % Print the sidebar




\hypertarget{experience}{%
\section{Experience}\label{experience}}

\medskip

\nopagebreak

\begin{twenty}
    \twentyitem{Aug 2022 - Present}{\emph{Postdoctoral Research Fellow}}{University of South Carolina}{Columbia, South Carolina\par\begin{minipage}{0.95\textwidth}%
\begin{itemize}%
\item Conducted advanced statistical analyses and data wrangling in R for academic manuscripts related to early childhood motor and cognitive development.%
\item Applied innovative data processing techniques, enhancing sensitivity to developmental changes, resulting in 1 peer-reviewed manuscript (in-review) and an international conference presentation.%
\item Collaborated with cross-functional teams to conduct statistical analyses, optimize data processing, and efficiently manage data for ongoing research projects.%
\item Managed project workflows on GitHub, optimizing research processes for academic publications.%
\end{itemize}%
\end{minipage}}
    \twentyitem{Aug 2019 - Aug 2022}{\emph{Doctoral Graduate Assistant}}{University of South Carolina}{Columbia, South Carolina\par\begin{minipage}{0.95\textwidth}%
\begin{itemize}%
\item Managed, cleaned, and created predictive models for longitudinal participant data, leading to the publication of 5 peer-reviewed manuscripts and 6 international presentations.%
\item Automated data processing with custom R scripts, saving 42 hours across 8 data collections.%
\item Parsed thousands of data points, extracting custom indices to establish longitudinal markers for motor and cognitive performance in ROTC Cadets.%
\end{itemize}%
\end{minipage}}
\end{twenty}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-R-vitae}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{O'Hara-Wild, M., \& Hyndman, R. (2023). \emph{Vitae:
Curriculum vitae for r markdown}.
\url{https://CRAN.R-project.org/package=vitae}}

\leavevmode\vadjust pre{\hypertarget{ref-R-tibble}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Müller, K., \& Wickham, H. (2023). \emph{Tibble: Simple
data frames}. \url{https://CRAN.R-project.org/package=tibble}}

\hypertarget{education}{%
\section{Education}\label{education}}

\nopagebreak

\begin{twenty}
    \twentyitem{2019 - 2022}{PhD -- Motor Behavior}{University of South Carolina}{Columbia, South Carolina\par\empty}
    \twentyitem{2017 - 2019}{MAT -- Physical Education}{University of South Carolina}{Columbia, South Carolina\par\empty}
    \twentyitem{2013 - 2017}{BS -- Exercise Science}{Lander University}{Greenwood, South Carolina\par\empty}
\end{twenty}


\end{document}
